### 2019-01-13 papers/journal/encoding.tex
Fancy lookign table

\input{satqbf-table}
%
In the table~\ref{tab:satqbf-graph}, you can see that SAT version was not able to scale it to the desired results.
%
This can be due to the fact that directly translating a quantified formula into a quantifier-free  by introducing a vector of variables for each boolean possibility will blow up the size of the formula and may not be solvable by a SAT solver.

>>>>

\input{satqbf-table}
%
The table~\ref{tab:satqbf-graph}, shows results of search result of universal condition for N = 5, 3-connected graphs. The SAT version was not able to scale it to the desired results and either timed-out (T/O) or ran out of memory (M/O).
%
This can be due to the fact that directly translating a quantified formula into a quantifier-free  by introducing a vector of variables for each boolean possibility will blow up the size of the formula and may not be solvable by a SAT solver.
